A Quantitative Study of Finnish Knowledge Production `r params$min.year`-`r params$max.year`

### 2016-07-27 inst/examples/manuscript-krakow.Rmd
Rmd update

---
title: "Digital History in Finland, 1488-1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "`r Sys.Date()`"
bibliography: 
- bibliography.bib
- references.bib
output: 
  md_document:
    variant: markdown_github
---
<!--
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{microbiome tutorial}
  %\usepackage[utf8]{inputenc}
-->

>>>>

---
title: "Digital History in Finland, 1488-1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "`r Sys.Date()`"
bibliography: 
- bibliography.bib
- references.bib
output: 
  md_document:
    variant: markdown_github
  pdf_document:
    citation_package: natbib
    keep_tex: true
---
<!--
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{microbiome tutorial}
  %\usepackage[utf8]{inputenc}
-->

### 2016-07-27 inst/examples/slidetemplates.Rmd
Rmd update

---
title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "`r Sys.Date()`"
output: 
  beamer_presentation:
    theme: "boxes"
    colortheme: "orchid"
    fonttheme: "professionalfonts"
fontsize: 13pt
---

```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE}
# Default time span
min.year <- 1488
max.year <- 1828

@@

```{r 201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE}
# Full combined catalogue (Fen + Kun) with marked duplicates
df.combined.preprocessed <- readRDS("df.combined.Rds")
# Data with duplicates removed and years limited
df0 <- df.combined.preprocessed %>% filter(!remove) %>%
	   			    filter(publication_year >= min.year &
					   publication_year <= max.year)
```

@@

**Idea**: Study early modern knowledge production, all of it (1470-1830)

**How?** Combine library catalogues (Fennica, Kungliga, ESTC, CERL HPB database)

>>>>

---
title: "A Quantitative Study of Finnish Knowledge Production `r params$min.year`-`r params$max.year`"
subtitle: "Subtitle here"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "`r Sys.Date()`"
fontsize: 13pt
geometry: margin=1in
linkcolor: magenta
urlcolor: blue
citecolor: black
institute: "University of Helsinki"
output: 
  beamer_presentation:
    theme: "boxes"
    colortheme: "orchid"
    fonttheme: "professionalfonts"
  pdf_document:
    fig_width: 7
    fig_height: 6
    fig_caption: true
    includes:
      in_header: header.tex
params:
  min.year: 
    label: "Start year:"
    input: numeric
    value: 1488
  max.year: 
    label: "End year:"
    input: numeric
    value: 1828
  journals:
    label: "Include journals:"
    value: TRUE
    input: checkbox
  catalogue:
    label: "Library catalog:"
    value: all
    input: select
    multiple: TRUE
    choices: [fennica, kungliga, all]
  language:
    label: "Language:"
    value: all
    input: radio
    choices: [finnish, swedish, all]
  data: 
    label: "Input dataset:"
    value: df.combined.Rds
    input: file
  slideparameter: 
    label: "Sliding value:"
    value: 100
    input: slider
    min: 0
    max: 1000
  date: 
    label: "Date:"
    value: !r date()
    input: date
  text: 
    label: "Text:"
    value: Some test text
    input: text
---

```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE}

# For all parameter options for rmarkdown slide rendering, see:
# http://rmarkdown.rstudio.com/developer_parameterized_reports.html
# More header options in Pandoc manual
# http://pandoc.org/MANUAL.html#templates

# Read parameters from the header
mydate <- params$start
min.year <- params$min.year
max.year <- params$max.year

@@

```{r 201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE}
# Full combined catalogue (Fen + Kun) with marked duplicates
#df.combined.preprocessed <- readRDS("df.combined.Rds")
df.combined.preprocessed <- readRDS(params$data)
# Data with duplicates removed and years limited
df0 <- df.combined.preprocessed %>% filter(!remove) %>%
	   			    filter(publication_year >= min.year &
					   publication_year <= max.year)

if (!params$catalogue == "all") {
  df0 <- filter(df0, catalog == params$catalogue)
}
```

@@

**Idea**: Study early modern knowledge production, all of it (`r min.year`-`r max.year`)  
**How?** Combine library catalogues (Fennica, Kungliga, ESTC, CERL HPB database)
